---
title: "R Notebook"
output: html_notebook
---

## Notebook

- Record the statistical results for FIGO, MAGiC Project;
- Dataset (109 cases) last updated on Dec 09, 2021;
- Some values are missing; 
- Excluded cases(artifacts)
- 004, 016, 023, 034, 063, 079


### Statistical Methods

1. Mann-Whitney U test

- test the difference between mean values of two subgroups 
- for non-normal distribution

2. Kruskal–Wallis test

- test whether the population distributions are identical between two or more subgroups
- H0: the subgroups are from identical populations


### 0. Load dataset from excel
```{r}
# import required packages
library(readxl)
library(ggplot2)
library(pROC)
library(stringr)
library(outliers)
library(DescTools)


# load data from excel
df1 <- read_excel("./Qvalues_0830.xlsx", sheet = "Sheet1")
df2 <- read_excel("./Qvalues_0830.xlsx", sheet = "Sheet2")

df <- df1
df[, 2:9] <- (df1[, 2:9] + df2[, 2:9])/2
df$FIGO3 <- str_replace_all(df$stage, c("3a" = "o", "3b" = "o", "3c1" = "o", "3c2" = "o", "4" = "o", "2" = "o", "3" = "o"))
df <- df[complete.cases(df[, c("FIGO3")]), ]

df_figo1 <- subset(df, FIGO3 == '1a')
df_figo2 <- subset(df, FIGO3 == '1b')
df_figo3 <- subset(df, FIGO3 == 'o')
df_figo23 <- subset(df, FIGO3 != '1a')
df_figo12 <- subset(df, FIGO3 != 'o')
```


```{r}
MedianCI(df_figo1$T1, conf.level = 0.95, na.rm = TRUE)
MedianCI(df_figo1$T2, conf.level = 0.95, na.rm = TRUE)
MedianCI(df_figo1$PD, conf.level = 0.95, na.rm = TRUE)
MedianCI(df_figo1$ADC, conf.level = 0.95, na.rm = TRUE)

MedianCI(df_figo2$T1, conf.level = 0.95, na.rm = TRUE)
MedianCI(df_figo2$T2, conf.level = 0.95, na.rm = TRUE)
MedianCI(df_figo2$PD, conf.level = 0.95, na.rm = TRUE)
MedianCI(df_figo2$ADC, conf.level = 0.95, na.rm = TRUE)

MedianCI(df_figo3$T1, conf.level = 0.95, na.rm = TRUE)
MedianCI(df_figo3$T2, conf.level = 0.95, na.rm = TRUE)
MedianCI(df_figo3$PD, conf.level = 0.95, na.rm = TRUE)
MedianCI(df_figo3$ADC, conf.level = 0.95, na.rm = TRUE)

```


```{r T1}

kruskal.test(T1 ~ FIGO3, data = df)

wilcox.test(df_figo1$T1, df_figo2$T1, exact=FALSE)
wilcox.test(df_figo1$T1, df_figo3$T1, exact=FALSE)
wilcox.test(df_figo2$T1, df_figo3$T1, exact=FALSE)

wilcox.test(df_figo1$T1, df_figo23$T1, exact=FALSE)
wilcox.test(df_figo12$T1, df_figo3$T1, exact=FALSE)

```


```{r T2}

kruskal.test(T2 ~ FIGO3, data = df)

wilcox.test(df_figo1$T2, df_figo2$T2, exact=FALSE)
wilcox.test(df_figo1$T2, df_figo3$T2, exact=FALSE)
wilcox.test(df_figo2$T2, df_figo3$T2, exact=FALSE)

wilcox.test(df_figo1$T2, df_figo23$T2, exact=FALSE)
wilcox.test(df_figo12$T2, df_figo3$T2, exact=FALSE)
```


```{r PD}

kruskal.test(PD ~ FIGO3, data = df)

wilcox.test(df_figo1$PD, df_figo2$PD, exact=FALSE)
wilcox.test(df_figo1$PD, df_figo3$PD, exact=FALSE)
wilcox.test(df_figo2$PD, df_figo3$PD, exact=FALSE)

wilcox.test(df_figo1$PD, df_figo23$PD, exact=FALSE)
wilcox.test(df_figo12$PD, df_figo3$PD, exact=FALSE)
```


```{r ADC}

kruskal.test(ADC ~ FIGO3, data = df)

wilcox.test(df_figo1$ADC, df_figo2$ADC, exact=FALSE)
wilcox.test(df_figo1$ADC, df_figo3$ADC, exact=FALSE)
wilcox.test(df_figo2$ADC, df_figo3$ADC, exact=FALSE)

wilcox.test(df_figo1$ADC, df_figo23$ADC, exact=FALSE)
wilcox.test(df_figo12$ADC, df_figo3$ADC, exact=FALSE)
```



