---
title: "R Notebook"
output: html_notebook
---

## Notebook

- Record the statistical results for grade, MAGiC Project;
- Dataset (109 cases) last updated on Dec 09, 2021;
- Some values are missing; 
- Excluded cases(artifacts)
- 004, 016, 023, 034, 063, 079


### Statistical Methods

1. Mann-Whitney U test

- test the difference between mean values of two subgroups 
- for non-normal distribution

2. Kruskal–Wallis test

- test whether the population distributions are identical between two or more subgroups
- H0: the subgroups are from identical populations


### 0. Load dataset from excel
```{r}

# import required packages
library(readxl)
library(ggplot2)
library(pROC)
library(stringr)
library(outliers)
library(DescTools)


# load data from excel
df1 <- read_excel("./Qvalues_0830.xlsx", sheet = "Sheet1")
df2 <- read_excel("./Qvalues_0830.xlsx", sheet = "Sheet2")

df <- df1
df[, 2:9] <- (df1[, 2:9] + df2[, 2:9])/2
df <- df[complete.cases(df[, c("Grade")]), ]

df_gra1 <- subset(df, Grade == 1)
df_gra2 <- subset(df, Grade == 2)
df_gra3 <- subset(df, Grade == 3)
df_gra23 <- subset(df, Grade > 1)
df_gra12 <- subset(df, Grade < 3)


MedianCI(df_gra1$T1, conf.level = 0.95, na.rm = TRUE)
MedianCI(df_gra1$T2, conf.level = 0.95, na.rm = TRUE)
MedianCI(df_gra1$PD, conf.level = 0.95, na.rm = TRUE)
MedianCI(df_gra1$ADC, conf.level = 0.95, na.rm = TRUE)

MedianCI(df_gra23$T1, conf.level = 0.95, na.rm = TRUE)
MedianCI(df_gra23$T2, conf.level = 0.95, na.rm = TRUE)
MedianCI(df_gra23$PD, conf.level = 0.95, na.rm = TRUE)
MedianCI(df_gra23$ADC, conf.level = 0.95, na.rm = TRUE)
```


```{r T1}
# boxplot(df$T1 ~ df$Grade)
kruskal.test(T1 ~ Grade, data = df)

wilcox.test(df_gra1$T1, df_gra2$T1, exact=FALSE)
wilcox.test(df_gra1$T1, df_gra3$T1, exact=FALSE)
wilcox.test(df_gra2$T1, df_gra3$T1, exact=FALSE)

wilcox.test(df_gra1$T1, df_gra23$T1, exact=FALSE)
wilcox.test(df_gra12$T1, df_gra3$T1, exact=FALSE)


MedianCI(df_gra1$T1, conf.level = 0.95, na.rm = TRUE)
MedianCI(df_gra23$T1, conf.level = 0.95, na.rm = TRUE)

```


```{r T2}
# boxplot(df_gra$T2 ~ df_gra$Grade)
kruskal.test(T2 ~ Grade, data = df)

wilcox.test(df_gra1$T2, df_gra2$T2, exact=FALSE)
wilcox.test(df_gra1$T2, df_gra3$T2, exact=FALSE)
wilcox.test(df_gra2$T2, df_gra3$T2, exact=FALSE)

wilcox.test(df_gra1$T2, df_gra23$T2, exact=FALSE)
wilcox.test(df_gra12$T2, df_gra3$T2, exact=FALSE)
```


```{r PD}
# boxplot(df_gra$PD ~ df_gra$Grade)
kruskal.test(PD ~ Grade, data = df)

wilcox.test(df_gra1$PD, df_gra2$PD, exact=FALSE)
wilcox.test(df_gra1$PD, df_gra3$PD, exact=FALSE)
wilcox.test(df_gra2$PD, df_gra3$PD, exact=FALSE)

wilcox.test(df_gra1$PD, df_gra23$PD, exact=FALSE)
wilcox.test(df_gra12$PD, df_gra3$PD, exact=FALSE)
```


```{r ADC}
# boxplot(df_gra$ADC ~ df_gra$Grade)
kruskal.test(ADC ~ Grade, data = df)

wilcox.test(df_gra1$ADC, df_gra2$ADC, exact=FALSE)
wilcox.test(df_gra1$ADC, df_gra3$ADC, exact=FALSE)
wilcox.test(df_gra2$ADC, df_gra3$ADC, exact=FALSE)

wilcox.test(df_gra1$ADC, df_gra23$ADC, exact=FALSE)
wilcox.test(df_gra12$ADC, df_gra3$ADC, exact=FALSE)
```



