---
title: "Results of MAGiC for CSI, LVSI and risks, part 1"
output: html_notebook
---

Last modified: 08/30/2021; 

## Notebook

- Record the statistical results for grade, MAGiC Project;
- Dataset (109 cases) last updated on Dec 09, 2021;
- Some values are missing; 
- Excluded cases(artifacts)
- 004, 016, 023, 034, 063, 079


### Statistical Methods

1. Mann-Whitney U test

- test the difference between mean values of two subgroups 
- for non-normal distribution

2. Kruskal–Wallis test

- test whether the population distributions are identical between two or more subgroups
- H0: the subgroups are from identical populations


### 0. Load dataset from excel
```{r load data}
# import required packages
library(readxl)
library(ggplot2)
library(pROC)
library(stringr)
library(outliers)
library(DescTools)


df1 <- read_excel("./Qvalues_0830.xlsx", sheet = "Sheet1")
df2 <- read_excel("./Qvalues_0830.xlsx", sheet = "Sheet2")

df <- df1
df[, 2:9] <- (df1[, 2:9] + df2[, 2:9])/2

```


```{r}
# add a new column recording risk
df_risk = transform(df, risk=0)
# pick out cases with high risk
list_high = which(df$Histology == 2 | df$Histology == 3 | df$Grade == 3 | df$stage == '3a' | df$stage == '3b' | df$stage == '3c1' | df$stage == '3c2' | df$stage == '4' | df$stage == '3'); 
# list_high = which(df$Histology == 2 | df$Histology == 3 | df$Grade == 3 | df$staging == '3a' | df$staging == '3b' | df$staging == '3c1' | df$staging == '3c2' | df$staging == '4'); 

# cases with low risk: supplementary set
list_low = setdiff(c(1:nrow(df)), list_high)
# low risk: 0; high risk: 1;
df_risk[list_high, 'risk'] = 1 
```


```{r}
# 2nd risk definition
# add a new column recording risk
df_risk = transform(df, risk=0)
# pick out cases with low risk
list_low = which(df$Histology == 1 & df$Grade !=3  & df$CSI == 0 & df$LVSI == 0 & df$MI != 2); 

# cases with low risk: supplementary set
list_high = setdiff(c(1:nrow(df)), list_low)
# low risk: 0; high risk: 1;
df_risk[list_high, 'risk'] = 1 
```


```{r T1}
# remove rows with NA and others in CSI & T1 column
df_CSI <- df[complete.cases(df[, c("T1", "CSI")]), ]
# boxplot(df_CSI$T1 ~ df_CSI$CSI)
wilcox.test(T1~CSI, data = df_CSI, exact=FALSE)
df_CSI1 <- subset(df_CSI, CSI == 0)
df_CSI2 <- subset(df_CSI, CSI == 1)


MedianCI(df_CSI1$T1, conf.level = 0.95, na.rm = TRUE)
MedianCI(df_CSI2$T1, conf.level = 0.95, na.rm = TRUE)


# remove rows with NA and others in LVSI & T1 column
df_LVSI <- df[complete.cases(df[, c("T1", "LVSI")]), ]
# boxplot(df_LVSI$T1 ~ df_LVSI$LVSI)
wilcox.test(T1~LVSI, data = df_LVSI, exact=FALSE)
df_LVSI1 <- subset(df_LVSI, LVSI == 0)
df_LVSI2 <- subset(df_LVSI, LVSI == 1)

MedianCI(df_LVSI1$T1, conf.level = 0.95, na.rm = TRUE)
MedianCI(df_LVSI2$T1, conf.level = 0.95, na.rm = TRUE)


df_risk <- df_risk[complete.cases(df_risk[, c("T1", "risk")]), ]
df_risk1 <- subset(df_risk, risk == 0)
df_risk2 <- subset(df_risk, risk == 1)

wilcox.test(df_risk1$T1, df_risk2$T1, exact=FALSE)
MedianCI(df_risk1$T1, conf.level = 0.95, na.rm = TRUE)
MedianCI(df_risk2$T1, conf.level = 0.95, na.rm = TRUE)
```


```{r T2}
# remove rows with NA and others in CSI & T2 column
df_CSI <- df[complete.cases(df[, c("T2", "CSI")]), ]
# boxplot(df_CSI$T2 ~ df_CSI$CSI)
wilcox.test(T2~CSI, data = df_CSI, exact=FALSE)
df_CSI1 <- subset(df_CSI, CSI == 0)
df_CSI2 <- subset(df_CSI, CSI == 1)

MedianCI(df_CSI1$T2, conf.level = 0.95, na.rm = TRUE)
MedianCI(df_CSI2$T2, conf.level = 0.95, na.rm = TRUE)


# remove rows with NA and others in LVSI & T2 column
df_LVSI <- df[complete.cases(df[, c("T2", "LVSI")]), ]
# boxplot(df_LVSI$T2 ~ df_LVSI$LVSI)
wilcox.test(T2~LVSI, data = df_LVSI, exact=FALSE)
df_LVSI1 <- subset(df_LVSI, LVSI == 0)
df_LVSI2 <- subset(df_LVSI, LVSI == 1)

MedianCI(df_LVSI1$T2, conf.level = 0.95, na.rm = TRUE)
MedianCI(df_LVSI2$T2, conf.level = 0.95, na.rm = TRUE)


df_risk <- df_risk[complete.cases(df_risk[, c("T2", "risk")]), ]
df_risk1 <- subset(df_risk, risk == 0)
df_risk2 <- subset(df_risk, risk == 1)

wilcox.test(df_risk1$T2, df_risk2$T2, exact=FALSE)
MedianCI(df_risk1$T2, conf.level = 0.95, na.rm = TRUE)
MedianCI(df_risk2$T2, conf.level = 0.95, na.rm = TRUE)
```


```{r PD}
# remove rows with NA and others in CSI & PD column
df_CSI <- df[complete.cases(df[, c("PD", "CSI")]), ]
# boxplot(df_CSI$PD ~ df_CSI$CSI)
wilcox.test(PD~CSI, data = df_CSI, exact=FALSE)
print("--------------------------")
df_CSI1 <- subset(df_CSI, CSI == 0)
df_CSI2 <- subset(df_CSI, CSI == 1)
MedianCI(df_CSI1$PD, conf.level = 0.95, na.rm = TRUE)
MedianCI(df_CSI2$PD, conf.level = 0.95, na.rm = TRUE)


# remove rows with NA and others in LVSI & PD column
df_LVSI <- df[complete.cases(df[, c("PD", "LVSI")]), ]
# boxplot(df_LVSI$PD ~ df_LVSI$LVSI)
wilcox.test(PD~LVSI, data = df_LVSI, exact=FALSE)
df_LVSI1 <- subset(df_LVSI, LVSI == 0)
df_LVSI2 <- subset(df_LVSI, LVSI == 1)
MedianCI(df_LVSI1$PD, conf.level = 0.95, na.rm = TRUE)
MedianCI(df_LVSI2$PD, conf.level = 0.95, na.rm = TRUE)


df_risk <- df_risk[complete.cases(df_risk[, c("PD", "risk")]), ]
df_risk1 <- subset(df_risk, risk == 0)
df_risk2 <- subset(df_risk, risk == 1)

wilcox.test(df_risk1$PD, df_risk2$PD, exact=FALSE)
MedianCI(df_risk1$PD, conf.level = 0.95, na.rm = TRUE)
MedianCI(df_risk2$PD, conf.level = 0.95, na.rm = TRUE)
```


```{r ADC}
# remove rows with NA and others in CSI & ADC column
df_CSI <- df[complete.cases(df[, c("ADC", "CSI")]), ]
# boxplot(df_CSI$ADC ~ df_CSI$CSI)
wilcox.test(ADC~CSI, data = df_CSI, exact=FALSE)
df_CSI1 <- subset(df_CSI, CSI == 0)
df_CSI2 <- subset(df_CSI, CSI == 1)
MedianCI(df_CSI1$ADC, conf.level = 0.95, na.rm = TRUE)
MedianCI(df_CSI2$ADC, conf.level = 0.95, na.rm = TRUE)


# remove rows with NA and others in LVSI & ADC column
df_LVSI <- df[complete.cases(df[, c("ADC", "LVSI")]), ]
# boxplot(df_LVSI$ADC ~ df_LVSI$LVSI)
wilcox.test(ADC~LVSI, data = df_LVSI, exact=FALSE)
df_LVSI1 <- subset(df_LVSI, LVSI == 0)
df_LVSI2 <- subset(df_LVSI, LVSI == 1)
MedianCI(df_LVSI1$ADC, conf.level = 0.95, na.rm = TRUE)
MedianCI(df_LVSI2$ADC, conf.level = 0.95, na.rm = TRUE)


df_risk <- df_risk[complete.cases(df_risk[, c("ADC", "risk")]), ]
df_risk1 <- subset(df_risk, risk == 0)
df_risk2 <- subset(df_risk, risk == 1)

wilcox.test(df_risk1$ADC, df_risk2$ADC, exact=FALSE)
MedianCI(df_risk1$ADC, conf.level = 0.95, na.rm = TRUE)
MedianCI(df_risk2$ADC, conf.level = 0.95, na.rm = TRUE)
```