---
title: "Summary of the dataset"
output: html_notebook
---

## Notebook

- Record the statistical results for grade, MAGiC Project;
- Dataset (109 cases) last updated on Dec 09, 2021;
- Some values are missing; 
- Excluded cases(artifacts)
- 004, 016, 023, 034, 063, 079


### Statistical Methods

1. Mann-Whitney U test

- test the difference between mean values of two subgroups 
- for non-normal distribution

2. Kruskal–Wallis test

- test whether the population distributions are identical between two or more subgroups
- H0: the subgroups are from identical populations


### 0. Load dataset from excel
```{r}

library(readxl)
library(ggplot2)
library(pROC)
library(stringr)
library(outliers)
library(psych)
library(irr)


# load data from excel
df1 <- read_excel("./Qvalues_0830.xlsx", sheet = "Sheet1")
df2 <- read_excel("./Qvalues_0830.xlsx", sheet = "Sheet2")

df <- df1
# average results from two reviewers
df[, 2:9] <- (df1[, 2:9] + df2[, 2:9])/2
```


```{r}
df_T1 <- data.frame(R1=df1$T1, R2=df2$T1)
ICC(df_T1)
icc(df_T1, model = c("twoway"), type = c("agreement"), unit = c("average"))
```


```{r}
df_T2 <- data.frame(R1=df1$T2, R2=df2$T2)
ICC(df_T2)
icc(df_T2, model = c("twoway"), type = c("agreement"), unit = c("average"))
```

```{r}
df_PD <- data.frame(R1=df1$PD, R2=df2$PD)
ICC(df_PD)
icc(df_PD, model = c("twoway"), type = c("agreement"), unit = c("average"))
```


```{r}
df_ADC <- data.frame(R1=df1$ADC, R2=df2$ADC)
ICC(df_ADC)
icc(df_ADC, model = c("twoway"), type = c("agreement"), unit = c("average"))
```




```{r}
summary_def <- function(x,na.omit=FALSE){
                         if(na.omit)
                          x <- x[!is.na(x)]
                         m <- mean(x)
                         n <- length(x)
                         s <- sd(x)
                         min_x <- min(x)
                         max_x <- max(x)
                         return(c(n=n,mean=m,stdev=s,min=min_x,max=max_x))}

sapply(df[c("T1")], summary_def)
sapply(df[c("T2")], summary_def)
sapply(df[c("PD")], summary_def)
sapply(df[c("ADC")], summary_def)
```

``` {r}
mean(df$age)
sd(df$age)
```