---
title: "Results of MAGiC for MI, part 1"
output: html_notebook
---

Last modified: 08/30/2021; 

## Notebook

- Record the statistical results for grade, MAGiC Project;
- Dataset (109 cases) last updated on Dec 09, 2021;
- Some values are missing; 
- Excluded cases(artifacts)
- 004, 016, 023, 034, 063, 079


### Statistical Methods

1. Mann-Whitney U test

- test the difference between mean values of two subgroups 
- for non-normal distribution

2. Kruskal–Wallis test

- test whether the population distributions are identical between two or more subgroups
- H0: the subgroups are from identical populations


### 0. Load dataset from excel
```{r}

# import required packages
library(readxl)
library(ggplot2)
library(pROC)
library(stringr)
library(outliers)
library(DescTools)

# load data from excel
df1 <- read_excel("./Qvalues_0830.xlsx", sheet = "Sheet1")
df2 <- read_excel("./Qvalues_0830.xlsx", sheet = "Sheet2")

df <- df1
df[, 2:9] <- (df1[, 2:9] + df2[, 2:9])/2

df <- df[complete.cases(df[, c("MI")]), ]

df_MI_1 <- subset(df, MI == 0)
df_MI_2 <- subset(df, MI == 1)
df_MI_3 <- subset(df, MI == 2)
df_MI_23 <- subset(df, MI > 0)
df_MI_12 <- subset(df, MI < 2)

```


```{r}
MedianCI(df_MI_1$T1, conf.level = 0.95, na.rm = TRUE)
MedianCI(df_MI_1$T2, conf.level = 0.95, na.rm = TRUE)
MedianCI(df_MI_1$PD, conf.level = 0.95, na.rm = TRUE)
MedianCI(df_MI_1$ADC, conf.level = 0.95, na.rm = TRUE)
```


```{r}
MedianCI(df_MI_2$T1, conf.level = 0.95, na.rm = TRUE)
MedianCI(df_MI_2$T2, conf.level = 0.95, na.rm = TRUE)
MedianCI(df_MI_2$PD, conf.level = 0.95, na.rm = TRUE)
MedianCI(df_MI_2$ADC, conf.level = 0.95, na.rm = TRUE)
```


```{r}
MedianCI(df_MI_3$T1, conf.level = 0.95, na.rm = TRUE)
MedianCI(df_MI_3$T2, conf.level = 0.95, na.rm = TRUE)
MedianCI(df_MI_3$PD, conf.level = 0.95, na.rm = TRUE)
MedianCI(df_MI_3$ADC, conf.level = 0.95, na.rm = TRUE)
```



```{r T1}
# boxplot(df_T1$T1 ~ df_T1$MI)
kruskal.test(T1 ~ MI, data = df)
print("--------------------------")

# test of normal distribution 
# (if p<0.05, reject null hypothesis, non-normal distribution)
shapiro.test(df$T1)
shapiro.test(df_MI_1$T1)
shapiro.test(df_MI_2$T1)
shapiro.test(df_MI_3$T1)
shapiro.test(df_MI_12$T1)
shapiro.test(df_MI_23$T1)
print("--------------------------")

wilcox.test(df_MI_1$T1, df_MI_2$T1, exact=FALSE)
wilcox.test(df_MI_1$T1, df_MI_3$T1, exact=FALSE)
wilcox.test(df_MI_2$T1, df_MI_3$T1, exact=FALSE)
print("--------------------------")


wilcox.test(df_MI_1$T1, df_MI_23$T1, exact=FALSE)
wilcox.test(df_MI_12$T1, df_MI_3$T1, exact=FALSE)
```


```{r T2}
#boxplot(df_T2$T2 ~ df_T2$MI)
kruskal.test(T2 ~ MI, data = df)

# test of normal distribution 
# (if p<0.05, reject null hypothesis, non-normal distribution)
shapiro.test(df$T2)
shapiro.test(df_MI_1$T2)
shapiro.test(df_MI_2$T2)
shapiro.test(df_MI_3$T2)
shapiro.test(df_MI_12$T2)
shapiro.test(df_MI_23$T2)
print("--------------------------")

wilcox.test(df_MI_1$T2, df_MI_2$T2, exact=FALSE)
wilcox.test(df_MI_1$T2, df_MI_3$T2, exact=FALSE)
wilcox.test(df_MI_2$T2, df_MI_3$T2, exact=FALSE)
print("--------------------------")


wilcox.test(df_MI_1$T2, df_MI_23$T2, exact=FALSE)
wilcox.test(df_MI_12$T2, df_MI_3$T2, exact=FALSE)
```


```{r PD}
#boxplot(df_MI$PD ~ df_MI$MI)
kruskal.test(PD ~ MI, data = df)

# test of normal distribution 
# (if p<0.05, reject null hypothesis, non-normal distribution)
shapiro.test(df$PD)
shapiro.test(df_MI_1$PD)
shapiro.test(df_MI_2$PD)
shapiro.test(df_MI_3$PD)
shapiro.test(df_MI_12$PD)
shapiro.test(df_MI_23$PD)
print("--------------------------")

wilcox.test(df_MI_1$PD, df_MI_2$PD, exact=FALSE)
wilcox.test(df_MI_1$PD, df_MI_3$PD, exact=FALSE)
wilcox.test(df_MI_2$PD, df_MI_3$PD, exact=FALSE)
print("--------------------------")

wilcox.test(df_MI_1$PD, df_MI_23$PD, exact=FALSE)
wilcox.test(df_MI_12$PD, df_MI_3$PD, exact=FALSE)
```


```{r ADC}
# boxplot(df_ADC$ADC ~ df_ADC$MI)
kruskal.test(ADC ~ MI, data = df)

# test of normal distribution 
# (if p<0.05, reject null hypothesis, non-normal distribution)
shapiro.test(df$ADC)
shapiro.test(df_MI_1$ADC)
shapiro.test(df_MI_2$ADC)
shapiro.test(df_MI_3$ADC)
shapiro.test(df_MI_12$ADC)
shapiro.test(df_MI_23$ADC)
print("--------------------------")

wilcox.test(df_MI_1$ADC, df_MI_2$ADC, exact=FALSE)
wilcox.test(df_MI_1$ADC, df_MI_3$ADC, exact=FALSE)
wilcox.test(df_MI_2$ADC, df_MI_3$ADC, exact=FALSE)

wilcox.test(df_MI_1$ADC, df_MI_23$ADC, exact=FALSE)
wilcox.test(df_MI_12$ADC, df_MI_3$ADC, exact=FALSE)
```



